Uniform formula lower bounds for finding and counting satisfiable assignments

### 2022-05-19 article/main.tex
Another day

\newcommand{\NN}{\mathbb{N}}%
\newcommand{\ZZ}{\mathbb{Z}}%
\newcommand{\Sbb}{\mathbb{S}}%
\newcommand{\Cc}{\mathcal{C}}%
\newcommand{\Gg}{\mathcal{G}}%
\newcommand{\Ss}{\mathcal{S}}%
\newcommand{\eps}{\varepsilon}%
\newcommand{\epsm}{\eps^{-1}}%
\newcommand{\bit}{\{0,1\}}%
\DeclareMathOperator*{\poly}{poly}

@@

\newcommand{\Poly}{\textsf{P}}%
\newcommand{\NP}{\textsf{NP}}%
\newcommand{\SAT}{\textsf{SAT}}%
\newcommand{\NAND}{\textsf{NAND}}%

@@

>>>>

\newcommand{\NN}{\mathbb{N}}%
\newcommand{\ZZ}{\mathbb{Z}}%
\newcommand{\Sbb}{\mathbb{S}}%
\newcommand{\Cc}{\mathcal{C}}%
\newcommand{\Gg}{\mathcal{G}}%
\newcommand{\Ff}{\mathcal{F}}%
\newcommand{\Ss}{\mathcal{S}}%
\newcommand{\eps}{\varepsilon}%
\newcommand{\epsm}{\eps^{-1}}%
\newcommand{\bit}{\{0,1\}}%
\DeclareMathOperator*{\poly}{poly}

@@

\newcommand{\Poly}{\textsf{P}}%
\newcommand{\NP}{\textsf{NP}}%
\newcommand{\NTIME}{\textsf{NTIME}}%
\newcommand{\SAT}{\textsf{SAT}}%
\newcommand{\ParSAT}{\ensuremath\bigoplus\textsf{SAT}}%
\newcommand{\SharpSAT}{\#\textsf{SAT}}%
\newcommand{\NAND}{\textsf{NAND}}%

@@

Slowdown Rule from algorithms for SAT assumptions:
\begin{lemma}
	Let $\Ff$ be a class of formulas closed under composition that can simulate projections in constant depth.
	If $\SAT\in \Ff[c \log n]$, then $\NTIME[n] \subseteq \Ff[c \log n]$.
\end{lemma}
\begin{proof}
	This follows from the fact that $\SAT$ is \NP-complete under uniform poly-log time first-order projections.
\end{proof}

Can we say the same for $\ParSAT$ and $\SharpSAT$?
